---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(rts)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rts

<!-- badges: start -->
<!-- badges: end -->

The goal of rts is to get data from the [Return to School Project](http://returntoschoolproject.org/) into R in a variety of forms. It is designed for internal use for the project and not likely useful outside of the project.

## Installation

You can install the package from R via
``` r
# install.packages("remotes") # if not previously installed
remotes::install_github("datalorax/rts")
```

## Usage

You first need to have an API key for the specific project. 

You first need to make sure you have a key to access the web API housing the 
data. The **rts** package includes helper functions for working with your key. 
First, store your key in your `.Renviron` using the following code, 
swapping the text for your specific key.

```{r eval = FALSE}
library(rts)
redcap_set_key(key = "mykeyabcdefg")
```

This will write a key to your `.Renviron` that is accessible via 
`redcap_key()`. You should only need to do this once, and you will need to 
make sure you restart your R session for the change to take effect. 
Generally, you won't need to access your key, but if for any reason you do, 
you can always run `redcap_key()` and your key will be printed to the console.

## Accessing data
Once you've set your key, you can access data from the project with the
`get_rts_data()` function. 

```{r example, message = FALSE}
d <- get_rts_data()

nrow(d)
ncol(d)
```

At this point, the only thing returned is a giant gnarly data frame 
that is not particularly useful, but future development will have it spit 
out the data for any survey and in a variety of different formats, based
on either specific argument to the function, or piping the data frame to 
new functions.
